Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-08-25 analysis/paper/paper.Rmd
Remove statement about grey intervals as they don't appear in figure

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was undecided on any detectable effects of impact factor. Intervals in grey indicate that the median was less than zero or less likely that code or data were shared and intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_h1), show_lables = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")

>>>>

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was undecided on any detectable effects of impact factor. Intervals in black indicate that the median value is above zero or more likely to share data and code.', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_h1), show_lables = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")
